---
  output: rmarkdown::github_document
---
### Background

`nazihuntR` : Tools to explore ZAŁOGA SS KL AUSCHWITZ data-store which contains information about Nazis who served at [Auschwitz](https://en.wikipedia.org/wiki/Auschwitz_concentration_camp)

Ref: <http://pamiec.pl/>

In January 2017 the [Krakow Rememberance Institute](https://en.wikipedia.org/wiki/Institute_of_National_Remembrance) published documents about the nearly 9,000 Nazi's who
worked at Auschwitz concentration camp.  This package builds an API wrapper around this data.  In addition, the package utilizes [Ryan Hafen](http://ryanhafen.com/blog/)'s incredible [trelliscopeJS](https://github.com/hafen/trelliscopejs) package to allow for interactive exploration of the 
data.

The packages allows you scrape the data real-time using the `get_nazis` function, this can take up to an hour depending on your internet speed.  As an alternative the `import_nazis` function provides real-time access to the data as of February 1st, 2017.

The package also provides links to documents, typically in German or Polish, for any Nazi's that have public records.

### Package functions

The following functions are implemented:

- `get_nazis`:	scrapes current data
- `import_nazis`:	imports cached data
- `visualize_nazis`: visualizes a trelliscope of the daa
- `tidy_counts`: tidy multiple count columns

### Installation

```{r eval=FALSE}
devtools::install_github("abresler/nazihuntR") 
devtools::install_github("hafen/trelliscopejs") # required for interactive analysis
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE, eval = FALSE}
library(nazihuntR)
library(dplyr)
get_nazis(parse_bios = TRUE, tidy_columns = FALSE, return_message = TRUE) ## scrapes
df_all <- 
nazihuntR::import_nazi_data(table_name = 'all') # returns cached table of all nazi data

df_names  <- 
nazihuntR::import_nazi_data(table_name = 'names') # returns cached table of all nazi names

df_items  <- 
nazihuntR::import_nazi_data(table_name = 'items') # returns cached table of all nazi fields with multiple items

nazihuntR::import_nazis(table_name = 'names', visualize_results = TRUE) # provides a trelliscope view

nazihuntR::import_nazis(table_name = 'items') %>% 
  visualize_nazis(title = "Nazis With Multiple Items")

```

#### Coming Soon

* Full data tidying
* Translations
* OCR of documents
* Image analysis tools
